Exploratory data analysis

### 2021-11-11 analysis/eda.Rmd
wflow_publish(knitr_in("analysis/eda.Rmd"), view = FALSE, verbose = TRUE)

  trees_with_bands,
  trees_with_bands_no_buffer
)
library("DataExplorer")
library("dplyr")
library("ggsci")
library("ggpubr")
library("ggplot2")
library("knitr")
library("purrr")
library("sp")
library("raster")
library("fs")
library("patchwork")
```

@@

```{r buffer-scenarios-1, echo=FALSE}
knitr::include_graphics("inst/tree-buffer-vis.png")
```

@@

```{r buffer-scenarios-2, echo=FALSE}
knitr::include_graphics("inst/tree-buffer-vis-max.png")
```

>>>>

  trees_with_bands,
  trees_with_bands_no_buffer
)
library("DataExplorer")
library("dplyr")
library("ggsci")
library("ggpubr")
library("ggplot2")
library("knitr")
library("purrr")
library("sp")
library("raster")
library("fs")
library("patchwork")
library("here")
```

@@

```{r buffer-scenarios-1, echo=FALSE}
knitr::include_graphics(here("docs/figure/tree-buffer-vis.png"))
```

@@

```{r buffer-scenarios-2, echo=FALSE}
knitr::include_graphics(here("docs/figure/tree-buffer-vis-max.png"))
```
